\texttt{\df} -- \\ modifying drafted figures\footnote{ For further information about the code visit \href{https://github.com/LukasCBossert/draftfigure}{https://github.com/LukasCBossert/draftfigure}: Comments and criticisms are welcome.}

### 2017-05-06 draftfigure.tex
documentation

% archaeologie --%
%            biblatex for archaeologists, 
%        historians and philologists
% Copyright (c) 2017 Lukas C. Bossert | Johannes Friedl
%  
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either version 1.3
% of this license or (at your option) any later version.
% The latest version of this license is in
%   http://www.latex-project.org/lppl.txt
% and version 1.3 or later is part of all distributions of LaTeX
% version 2005/12/01 or later.
% !TEX program = lualatex
\documentclass[a4paper,
10pt,
english
]{ltxdoc}
\input{archaeologie-preamble.tex}
\externaldocument{archaeologie-ger}[archaeologie-ger.pdf]% <- full or relative path

\begin{document}
\title{\texttt{archaeologie} -- \\\texttt{bib\LaTeX} for archaeologists\footnote{Also very handy for (ancient) History or Classics, too.
For further information about the code visit \href{http://www.biblatex-archaeologie.de}{biblatex-archaeologie.de}: 
Comments and criticisms are welcome.
We thank  ›moewew‹ and Herbert Voß for their big help on the code.%
}}
\author{Lukas C. Bossert\\{\small \href{mailto:info@biblatex-archaeologie.de}{info@biblatex-archaeologie.de}} 
\and Johannes Friedl}
\date{Version: \archaeologieversion{} (\archaeologiedate)} 
\maketitle

\begin{abstract}
\noindent This citation-style covers the citation and bibliography rules of the \DAI (DAI). 
Various options are available to change and adjust the outcome according to one's own preferences. 
The style is compatible with the English, German, Italian, Spanish and French languages, since all |bibstrings| used are defined in each language.
\bigskip

\noindent For a short introduction in German see   \href{pdfdeu.biblatex-archaeologie.de}{\textbf{online}} or   \href{file:archaeologie-ger.pdf}{\textbf{local}}.
\end{abstract}

\begin{multicols}{2}
\footnotesize\parskip=0mm \tableofcontents
\end{multicols}

\section{Installation}
|archaeologie| is part of the distributions MiK\TeX \footnote{Website: \url{http://www.miktex.org}.} 
and \TeX Live\footnote{Website: \url{http://www.tug.org/texlive}.}~-- thus, you
can easily install it using the respective package manager. 
If you would like to
install |archaeologie| manually, do the following:
Download the folder |archaeologie| with all relevant files from the CTAN-server\footnote{\url{https://www.ctan.org/pkg/archaeologie}} and copy the content of the |zip|-file to the \texttt{\$LOCALTEXMF} directory of
 your system.\footnote{If you don't know what that is, have a look at
\url{http://www.tex.ac.uk/cgi-bin/texfaq2html?label=tds} or 
\url{http://mirror.ctan.org/tds/tds.html}.} 
Refresh your filename database.\footnote{ 
Here is some additional information from the UK \TeX\ FAQ:
\begin{itemize}[nosep,after=\vspace{-\baselineskip} ]
  \item \href{%
    http://www.tex.ac.uk/cgi-bin/texfaq2html?label=install-where}{%
    Where to install packages}
  \item \href{%
    http://www.tex.ac.uk/cgi-bin/texfaq2html?label=inst-wlcf}{%
    Installing files \enquote{where \LaTeX /TeX\ can find them}}
  \item \href{%
    http://www.tex.ac.uk/cgi-bin/texfaq2html?label=privinst}{%
    \enquote{Private} installations of files}
\end{itemize}
}
%%introduction from biblatex-dw copied and applied. might to be rewritten.

\section{Usage}
 \DescribeMacro{archaeologie}  The name of the bib\LaTeX-style is  |archaeologie| which has to be activated in the preamble.

\begin{code}
\usepackage[style=archaeologie,%
          *@\meta{further options}@*]{biblatex}
\bibliography*@\marg{|bib|-file}@*
\end{code}

Without any further options the style follows the rules of the \DAI. 
No additional settings are needed,
but you can change the outcome by using some options which are explained below.\footnote{For an easy and unproblematic compiling we suggest to use \hologo{XeLaTeX} or  \hologo{LuaTeX}.}

At the end of your document you can write the command |\printbibliography| to print 
the bibliography. 
Since |archaeologie| supports different citations of various texts such as those of ancient authors and  modern scholars we suggest  having them listed in separate bibliographies. 
Further information can be found below   (\cref{bibliographie}).

\section{Overview}\label{overview}
There follows a quick overview of possible options of the style |archaeologie|. 
Contrary to the alphabetically ordered description later (\cref{options-description}) they here are listed by topic.
Furthermore you can -- at your own risk -- also use the conventional |bib|\LaTeX-options relating to indent, etc. 
For that please see the excellent documentation of  |bib|\LaTeX.

\subsection{Preamble options}\label{preamble_options}
\subsubsection{Additional bibliographies and macro lists}
\DescribeMacro{bibancient}A separate bibliography-file is loaded, in which round about 
600 ancient authors and works are listed and can be cited right away; cf. \cref{bibancient}.

\DescribeMacro{bibcorpora}
A separate bibliography-file is loaded, in which the common corpora for ancient studies are stored cf. \cref{bibcorpora}.
Additionally this activates the bibliography |archaeologie-lstabbrv.bib|.

\DescribeMacro{lstabbrv}
Activates the additional bibliography file |archaeologie-lstabbrv.bib|.
It provides a list of journals and series according to the abbreviations of the 
\DAI which can be used as |@String| macros in bibliography entries; cf. \cref{abbrv}.

\DescribeMacro{lstlocations}
Activates the additional bibliography file |archaeologie-lstlocations.bib|
with |@String| macros of locations which can be used to automatically print out their correct exonym in the selected language; cf. \cref{lstlocations}.

\DescribeMacro{lstpublishers}
Activates the additional bibliography file |archaeologie-lstpublishers.bib| with |@String| macros 
of several publishers which can be used to easily print out their names; cf. \cref{lstpublishers}.

\subsubsection{Notation of names}
\DescribeMacro{bibfullname}
In the bibliography full names of authors and/or editors are shown; cf. \cref{bibfullname}.

\DescribeMacro{citeauthorformat}
You can chose how the name of authors or editors are displayed within your text when they are cited with \cs{citeauthor}\marg{bibtex-key}.
You can chose between the options \meta{initials}, \meta{full}, \meta{family}, \meta{firstfull}; 
cf. \cref{citeauthorformat}.

\DescribeMacro{initials}
First names are abbreviated keeping digraphs and trigraphs (this is default); cf. \cref{initials}.

\DescribeMacro{scshape}
Cited names are shown with small capital letters cf. \cref{scshape}.
Bibliography entries with |option={ancient}| or |option={frgancient}| (\cref{ancient,frgancient}) are not affected by this option.

\subsubsection{Manner of citing}

\DescribeMacro{edby}
Switches \enquote{ed.}/\enquote{Hrsg.} to \enquote{ed. by}/\enquote{hrsg. v.}; cf. \cref{edby}.

\DescribeMacro{inreferences}
Each bibliography entry which is an |@Inreference| is fully referenced according to the special rules of the 
\DAI for manuals and encyclopaedias; cf. \cref{inreferences}.

\DescribeMacro{noabbrv}
By default the short titles of journals and series (|shortjournal| and |shortseries|) are shown in the bibliography.
With this option full titles are printed instead (|journaltitle| and |series|); cf. \cref{noabbrevs}.

\DescribeMacro{publisher}
All locations and the publisher is shown. 
It also changes the format of the edition and the first print; cf. \cref{publisher}.

\DescribeMacro{seenote}
By default |archaeologie| prints author-year-system. 
With this option you can change it to a different outcome (but still according to the rules of the \DAI). 
So the first citation will be a full citation and all the following citations will refer to the first full citation; cf. \cref{seenote}

\DescribeMacro{translation}
Original title, translator and original language are shown in the bibliography. 
Setting a bibliography entry to |option={ancient}| this behaviour is default; cf. \cref{translation}.

\DescribeMacro{yearinparens}
The year is shown in parentheses; cf. \cref{yearinparens}.

\DescribeMacro{yearseries}
Switches the order of series and year; cf. \cref{yearseries}.

\subsubsection{Global bibliography settings}

\DescribeMacro{width}
|width={value}| defines the bibliography width between label and reference; cf. \cref{width}.

\DescribeMacro{counter}
Reveals at the end of each reference a summary of citations in the text; cf. \cref{counter}.

\subsection{Entry Options}
A single bibliography entry can contain a value in its |options|-field.
Depending on the option it changes the behaviour of how that entry is cited; cf. \cref{options-bibentry,beispiele}. 
Beside their distinct properties all of these options have in common that the separating comma between citation and page record is missing. 
Actually this concerns citation of ancient texts and corpora where usually the |shorthand|-field is printed in citations.

\DescribeMacro{ancient}
The entry is an ancient source (e.\,g. Cicero, Plutarch, etc); cf. \cref{ancient}.

\DescribeMacro{frgancient}
The entry is a fragmentary ancient source (e.\,g. Festus); cf. \cref{frgancient}.

\DescribeMacro{corpus} 
Only the |shorthand|-field is printed.
This is needed especially for corpora of inscriptions or coins (CIL, AE, RIC, etc.); cf. \cref{corpus}.

\DescribeMacro{uniqueme} 
In cases there are different translations of an ancient work you can decide which one is the standard translation and which ones should be made unique by displaying the translator/series/editor; cf. \cref{uniqueme}.

\changes{v1.1}{2015/06/04}{New options added in summary.}

\subsection{Cite commands}\label{cite-commands}
\DescribeMacro{\cite}
As always citing is done with \cs{cite}:
\begin{code}
\cite*@\oarg{prenote}\oarg{postnote}\marg{bibtex-key}%@*
\end{code}

\meta{prenote} sets a short preliminary note (e.\,g. \enquote{Vgl.}) and \meta{postnote} is usually used for page numbers.
If only one optional argument is used then it is \oarg{postnote}.
\begin{code}
\cite*@\oarg{postnote}\marg{bibtex-key}%@*
\end{code}
The \meta{bibtex-key} corresponds to the key from the bibliography file.

\begin{example}
Public space is part of a city says \cite{Osland2016}.
\end{example}
\DescribeMacro{\cites}
If one wants to cite several authors or works a very convenient way is the following using the \cs{cites}-command:
\begin{code}
\cites(pre-prenote)(post-postnote)
  *@\oarg{prenote}\oarg{postnote}\marg{bibtex-key}@*%
  *@\oarg{prenote}\oarg{postnote}\marg{bibtex-key}@*%
  *@\oarg{prenote}\oarg{postnote}\marg{bibtex-key}\ldots@*
\end{code}
\begin{example}
Public space is part of a city say \cites(cf.)(){Osland2016}{Evangelidis2014}.
\end{example}

\DescribeMacro{\parencite}
Sometimes a citation has to be put in parentheses. 
Therefore we implemented the command \cs{parencite}:
\begin{code}
\parencite*@\oarg{postnote}\marg{bibtex-key}%@*
\end{code} 
This cite command takes care of the correct corresponding parentheses and brackets.
Especially in |@Inreference| citations the parentheses  change to (square) brackets.
The example shown in \cref{faq:inreference} makes it clear.
\begin{example}
Public space is part of a city \parencite{Osland2016}.
\end{example}

\DescribeMacro{\parencites}
Of course there is also the possibility to cite several authors/works in parentheses.
This is done with \cs{parencites}:
\begin{code}
\parencites(pre-prenote)(post-postnote)%
*@\oarg{prenote}\oarg{postnote}\marg{bibtex-key}@*%
*@\oarg{prenote}\oarg{postnote}\marg{bibtex-key}@*%
*@\oarg{prenote}\oarg{postnote}\marg{bibtex-key}\ldots@*
\end{code}
\begin{example}
Public space is part of a city \parencites(cf.)(){Osland2016}{Evangelidis2014}.
\end{example}

\DescribeMacro{\textcite}
Beside the listed \cs{cite} commands above there is a third way of citing:
\cs{textcite} is useful if the author should be mentioned in the text and
the remaining components such as year and page will immediately follow in parentheses. 
\begin{code}
\textcite*@\oarg{postnote}\marg{bibtex-key}%@*
\end{code}

\begin{example}
Public space is part of a city says \textcite{Osland2016}.
\end{example}

\DescribeMacro{\textcites}
And again there is also a \cs{textcites} in case of several authors: 
\begin{code}
\textcites(pre-prenote)(post-postnote)%
  *@\oarg{prenote}\oarg{postnote}\marg{bibtex-key}@*%
  *@\oarg{prenote}\oarg{postnote}\marg{bibtex-key}@*%
  *@\oarg{prenote}\oarg{postnote}\marg{bibtex-key}\ldots@*
\end{code}
\begin{example}
Public space is part of a city say \textcites{Osland2016}[cf.][]{Evangelidis2014}.
\end{example}

 \DescribeMacro{\footcite}
 Beside the listed \cs{cite} commands above there are more possibilities citing:
 There is also the possibility to put the citation into a footnote at once with \cs{footcite}:
 \begin{code}
\footcite*@\oarg{prenote}\oarg{postnote}\marg{bibtex-key}@*
\end{code}
\begin{example}
Public space is part of a city.\footcite{Osland2016}
\end{example}
This is the equivalent to |\footnote{\cite{Osland2016}.}| but it saves you a lot of time typing.
 \DescribeMacro{\footcites} And there is as well \cs{footcites}:
\begin{example}
Public space is part of a city.\footcites(cf.)(){Osland2016}{Evangelidis2014}
\end{example}

\DescribeMacro{\smartcite}
And there is also a clever way citing with \cs{smartcite}.
\cs{smartcite} depends on its environment it is used in. If it is your normal text it behaves like \cs{footcite} and will print the citation within a footnote.
If it is already within a footnote it will be handled like \cs{cite}. 
 is a clever 
\begin{code}
\smartcite*@\oarg{postnote}\marg{bibtex-key}%@*
\end{code}

\begin{example}
Public space is part of a city.\smartcite{Osland2016} 
And sometimes more than that.\footnote{\smartcite[cf.][]{Evangelidis2014}.}
\end{example}

\DescribeMacro{\smartcites}
And again there is also a \cs{textcites} in case of several authors: 
\begin{code}
\smartcites(pre-prenote)(post-postnote)%
  *@\oarg{prenote}\oarg{postnote}\marg{bibtex-key}@*%
  *@\oarg{prenote}\oarg{postnote}\marg{bibtex-key}@*%
  *@\oarg{prenote}\oarg{postnote}\marg{bibtex-key}\ldots@*
\end{code}
\begin{example}
Public space is part of a city.\smartcites{Osland2016}{Evangelidis2014} 
And sometimes more than that.\footnote{\smartcites{Osland2016}[cf.][]{Evangelidis2014}.}
\end{example}

\DescribeMacro{\autocite}
With \cs{autocite} there is a flexible way of citing. 
We set up \cs{autocite} as \cs{footcite} by default.
If you want to change it you can also write in the preamble e.\,g. |autocite=inline|.
\begin{code}
\autocite*@\oarg{prenote}\oarg{postnote}\marg{bibtex-key}%@*
\end{code}

\begin{example}
Public space is part of a city.\autocite{Osland2016} 
\end{example}

\DescribeMacro{\fullcite}\DescribeMacro{\footfullcite}
With \cs{fullcite} and \cs{footfullcite} you can print the complete entry in your current text.
\begin{code}
\fullcite*@\oarg{prenote}\oarg{postnote}\marg{bibtex-key}@*
\footfullcite*@\oarg{prenote}\oarg{postnote}\marg{bibtex-key}@*
\end{code}

\begin{example}
Public space is part of a city.\footfullcite{Osland2016}
As can be read in \fullcite{Evangelidis2014}
\end{example}

\DescribeMacro{\citeauthor}\DescribeMacro{\citetitle}\label{citeauthor}%
Furthermore and in addition to the ›normal‹ \cs{cite}-commands one can also cite only the author or the work title in the text and in the footnotes.
\begin{code}
\citeauthor*@\oarg{prenote}\oarg{postnote}\marg{bibtex-key}%@*
\end{code} 
  and for the works 
\begin{code}
\citetitle*@\oarg{prenote}\oarg{postnote}\marg{bibtex-key}%@*
\end{code}

\begin{example}
Public space is part of a city says \citeauthor{Osland2016} in \citetitle{Osland2016}.
\end{example}
For further information cf. \cref{citeauthorformat}.

\DescribeMacro{\citetranslator}\label{citetranslator}%
Addionally there is also a \cs{cite}-command which can be used to print the translator of an (ancient) work.
\begin{code}
\citetranslator*@\marg{bibtex-key}%@*
\end{code}
This will print the name(s) of the translator according to the chosen |citeauthorformat|.
If there is no translator it will name you as translator (\enquote{own translation}).
\begin{code}
\citetranslator* *@\marg{bibtex-key}%@*
\end{code} 
\newcommand\latquote[5]{\cite[#1][#2]{#3}: \emph{#4} -- \enquote{#5} \parentext{\citetranslator*{#3}}.}

The starred version prints also the informtion from which language the text has been translated.
For an efficient way of citing ancient texts we introduce a new command (only a suggestion):
\begin{code}
\newcommand\latquote[5]{\cite[#1][#2]{#3}: \emph{#4} -- \enquote{#5} \parentext{\citetranslator*{#3}}.}
\end{code}
\begin{example}
\latquote{cf.}{12,25,1}{Cic:Att}{sed domus est, ut ais, forum}{Aber dein Heim ist das Forum.}
\end{example}

\subsection{Entries with @String}\label{string}
The citation rules of the \DAI instruct to abbreviate journals and series according to a given list.\footnote{\url{http://www.dainst.org/documents/10180/70593/03_Liste+abzukürzender+Zeitschriften_quer.pdf} <2016-06-06>}
For this purpose we provide a list with bibliography macros which refer to these abbreviations. 
These abbreviations can be included by loading package option |lstabbrv| (cf. \cref{abbrv}). 
Besides there are two further lists with |@String| macros cf. \cref{lstpublishers,lstlocations}.

\DescribeMacro{@String} The style |archaeologie| respects the guidelines of the \DAI 
and is therefore compatible with the given abbreviations of journals and series.
To minimize the susceptibility to errors and to omit unnecessary typing of sometimes very long journal titles |archaeologie| works with so-called |@Strings|.
The advantage of these |@Strings| is that several bibliography entries can be defined by one globally given value. 
The |@String| is loaded at begin of the |bib|-file, therefore all |@Strings| have to be previous to all other bibliography entries.

To use this offer of simplification the following bibliography fields should be field with such a a |@String|: |journaltitle| and |shortjournal|,
(|series| and |shortseries|.
In \cref{abbrv-lists} there is a list with all the abbreviations given by the \DAI, 
in which the |@String| (with endings |-short| for |shortjournal| or |shortseries|) are listed in the left column.  
An |@String| has to be written \emph{without} any curly brackets.\footnote{If you use \emph{JabRef} in its non-coding window, 
then you have to write \#|AyasofyaMuezYil|\#. 
JabRef converts this internally to a |@String| and omits the \# in the coding window. 
\emph{BibDesk} provides such conversion as well by pressing
  %|cmd-R| 
\LKeyStrg + \LKey{R}
 which enables direct BibTeX typing without enclosing curly brackets.}

An example shows how to use it:

\begin{bibexample}[label=Koyunlu1990]{{@}Article\{Koyunlu1990,…\}}
@Article{Koyunlu1990,
  author       = {Koyunlu, A.},
  title        = {Die Bodenbelage und der Errichtungsort der Hagia Sophia},
  journaltitle = AyasofyaMuezYil,  %@String used
  shortjournal = AyasofyaMuezYil-short,  %@String used
  volume       = {11},
  pages        = {147--156},
  year         = {1990},
}
\end{bibexample}

That article appeared within a rather unusual journal, 
which should be abbreviated with ›AyasofyaMüzYıl‹.

To save  time  looking for the special character and insert ›ı‹ manually 
it is written in the |@String| with an ›i‹ (for further information see \cref{abbrv-lists}) but will be replaced after compiling with the correct character:

\printbib[6em]{Koyunlu1990}

Whether using the provided abbreviation list with |lstabbrv| or filling the |journaltitle| and |shortjournal| fields manually, 
|archaeologie| uses by default short titles if defined.
The default embedding of such abbreviations can be switched off, of course.
In case you use the package option |noabbrv| in the preamble (see \cref{noabbrevs}), then the output changes as follows:
\begin{bibbox}{Koyunlu1990}\footnotesize
\parbox[t]{2cm}{Koyunlu 1990} \parbox[t]{9cm}{A. Koyunlu, 
Die Bodenbelage und der Errichtungsort der Hagia Sophia, {\color{red}Ayasofia Müzesi yıllığı. Annual of Ayasofya Museum} 11, 1990, 147–156}
\end{bibbox}
Nevertheless the advantage of our abbreviation list lies in the possibility of creating a separate bibliography 
with all the abbreviations of used journal titles and series (see \cref{bibliographie}) without being prone to citation differences and typing errors.

However, if a journal or a series is \emph{not} included in the list (\cref{abbrv-lists}) 
then this journal/series will \emph{not} be abbreviated and converted to full title in curly brackets in the respective field e.\,g. |journaltitle=|\marg{title of the journal} or |series=|\marg{name of the series}. 
Therefore the field content will not be printed. 
At least |biblatex-biber| gives a warning in its log which can be checked.\footnote{For example something like \enquote{\enquote{journaltitle} in entry \meta{entrykey} cannot be null, deleting it}.}
For the following examples we use |@String| whenever it is appropriate and possible.

Lastly we want to point out that |@Strings| can also be used partly as following shows:

\begin{code}
@Incollection{Mundt2015,
  ...
  location     = Berlin #{ and Boston}, %@String partly used
  ...
}
\end{code}

Each time you want to leave the |@String| environment and enter the curly bracket environment (and reverse) make use of a hash \# to concatenate elements.

\section{Details of optional preferences}\label{options-description}
In the following  we give a more detailed insight into the various options of |archaeologie| 
and show their results on the bases of concrete examples.
Changes made by these options are {\color{red}coloured in red}.

\subsection{Preamble options}\label{options-preamble}
Optional preferences in the preamble are loaded within the package |bib|\LaTeX:
\begin{code}
\usepackage[%        
    backend=biber,  % activates biber (default; 
                    % but will give an error if not done)
    style=archaeologie,   % loads the style *@|archaeologie|@*
    inreferences=true,    % option *@|inreferences|@* is loaded
    lstabbrv              % option *@|lstabbrv|@* is loaded as well
    ]{biblatex}
\end{code}
In this example the style |archaeologie| is loaded with options |inreferences| and |lstabbrv|. 
Now, manual entries don't appear in author-year-style anymore and journal/series |@string|-macros are enabled.
By the way, it doesn't matter if you write |inreferences| or |inreferences=true|.

Each of the listed options is disabled by default even if we strongly recommend their use in particular the additional bibliographies and |@String| lists. 
All remaining options are rather a matter of taste.

Despite to the overview section (\cref{overview}) the following list is arranged in alphabetic order.

\subsubsection{bibancient}\label{bibancient}
\DescribeMacro{bibancient}
In case of citing ancient authors and their works you can do it with common \cs{cite}-commands.
Exclusively for this case we included a modification that respects the different citation of ancient authors and works.
With the option |bibancient| you load an additional bibliography called |archaeologie-bibancient.bib| in which we inserted almost 600 ancient authors and works with their abbreviation according to The New Pauly/Thesaurus Linguae Latinae.
For the complete list of those see \cref{list-bibancient}.
Using these pre-sets is recommended because it will guarantee a high level of consistency and minimize error-proneness.

You can cite the authors or works with their |bibtex-key| which you find in bold in the left column of the list. 
Authors and works are separated in the |bibtex-key| by a colon.
The entry on the right marks the |shorthand| which will be printed in your paper.

Let us make it clear with an example:

With the loaded option |bibancient| you can cite like this:

\begin{example}
\footnote{\cite[3,2,5--7]{Apul:met}.}
\end{example}

The corresponding bibliography-entry looks like this
\begin{bibexample}[label=Apul:met]{{@}Book\{Apul:met,…\}}
@Book{Apul:met,
  author      = {Apuleius Madaurensis, Lucius},
  title       = {metamorphoses},
  shorthand   = {Apul. met.},
  shortauthor = {Apuleius},
  keywords    = {ancient},
  options     = {ancient},
}
\end{bibexample}
All entries in the mentioned additional bibliography contain the line |keywords = {ancient}|.
With that you can print all ancient authors in a separated bibliography by typing:
\begin{code}
\printbibliography[keyword=ancient]
\end{code}
\printbib{Apul:met}

\begin{refsection}
By means of the |bibtexkey| (e.g. |Apul:met|) you can also cite only authors or titles like this:

\begin{example}
\citeauthor{Apul:met} remarks in \citetitle{Apul:met} ...
\end{example}

\end{refsection}

\changes{v1.5}{2016/05/31}{Extra Bibliographie}

\subsubsection{bibcorpora}\label{bibcorpora}
\DescribeMacro{bibcorpora}
This loads an additional bibliography which contains the most important corpora for ancient studies, so you can cite them right away in your document without creating a new bibentry by yourself. 
These corpora are listed in \cref{list-bibcorpora}. 
Advantage and usage mostly correspond to |bibancient|, 
so have a look at \cref{bibancient} for details.

\subsubsection{lstabbrv}\label{abbrv}
\DescribeMacro{lstabbrv}
If you want to benefit from the above mentioned method with |@String| (cf. \cref{string}) 
you have to activate the option called |lstabbrv| (list of abbreviations) in the preamble.
Once activated the additional bibliography |archaeologie-lstabbrv.bib| is loaded. 
In this bibliography all abbreviations listed in \cref{abbrv-lists} are stored; 
for further details of usage see \cref{string}.

\subsubsection{lstlocations}\label{lstlocations}
\DescribeMacro{lstlocations}
This loads an additional bibliography with |@Strings| of locations used to print out their correct exonym in the selected language. 
In that case you are not forced to change location spelling when switching the language. 
(Otherwise it is necessary to adjust location names like \emph{Rome} to \emph{Rom} or \emph{Roma} 
in your potentially multiple-used bibliography each time you change the language of your scientific text).
For details on the locations list, cf. \cref{list-locations}.

\subsubsection{lstpublishers}\label{lstpublishers}
\DescribeMacro{lstpublishers}
Activates the additional bibliography file |archaeologie-lstpublishers.bib| with |@Strings| 
of publishers which can be used to print out their correct name. 
Benefits are similar to the other lists mentioned above and in \cref{string}.
For the list, cf. \cref{list-publishers}

\subsubsection{seenote}\label{seenote}
\DescribeMacro{seenote}
Even if author-year-citation seems to be commonly accepted in Ancient Studies in the meantime you may want to use a traditional citation style. 
For this purpose you can switch to the other allowed citation rule by the \DAI
which works like this:
If you cite a work for the first time in a footnote |archaeologie| will print a full cite which contains all bibliography elements.
Henceforward each following citation is printed as short cite and will additionally refer to the footnote where the first cite was done.
Bibliography entries with |options={ancient}| are excluded from this speciality and are cited as always.

You can use the cite-commands \cs{cite(s)} and \cs{parencite(s)} but \cs{textcite(s)} 
will behave like \cs{cite(s)} because |seenote| actually just checks for occurrences in footnotes and does not refer to cites in running text.

We give an example:
\begin{tcolorbox}[examplebox] 
This is the first citation.|\footnote{\cite{Ball2013}.}|
This is one in between.|\footnote{anything in here.}|
And this is the third footnote and the second citation.|\footnote{\cite[470]{Ball2013}.}|
\tcblower
This is the first footnote.\footnote{L. F. Ball – J. J. Dobbins, Pompeii Forum Project. Current thinking on the Pompeii Forum, 117/3, 2013, 461–492.}
This is one in between.\footnote{anything in here.}
And this is the third footnote and the second citation.\footnote{Ball – Dobbins loc. cit. (see n. 1) 470.}
\end{tcolorbox}

\changes{v1.5}{2016/05/31}{Rückverweis}

\subsubsection{translation}\label{translation}
\DescribeMacro{translation}
Once this option is activated the original title, the original language and the translator of the work are printed (|origtitle|, |origlanguage|, |translator|).
For ancient texts and fragments (|options={ancient}| or |options={frgancient}|) this is default, 
so they will always be printed with original title, language and translator.

An example will clarify matters:
The bibliographical entry |Lefebvre2011| contains following fields:
\begin{bibexample}[label=Lefebvre2011]{{@}Book\{Lefebvre2011,…\}}
@Book{Lefebvre2011,
  author       = {Lefebvre,Henri},
  title        = {The Production of Space},
  publisher    = {Blackwell Publishing Ltd},
  location     = {Maien, MA and Oxford and Victoria},
  year         = {2011},
  edition      = {30},
  origlocation = {Oxford},
  origyear     = {1991},
  origtitle    = {La production de l’espace},
  origlanguage = {french},
  translator   = {Donald Nicholson-Smith},
}
\end{bibexample}

The bibliography result is:
\printbib[6em]{Lefebvre2011}

By activating option |translation| it will change to:

\begin{bibbox}{Lefebvre2011}\footnotesize
\parbox[t]{2cm}{Lefebvre 2011} \parbox[t]{9cm}{H. Lefebvre,  The Production of Space, 
{\color{red} La production de l’espace, trans. from French by D. Nicholson-Smith} \textsuperscript{30}(Oxford 1991; repr. Maien, MA 2011)}
\end{bibbox}

However, it works not only with entries like |@Book| but also with e.\,g. |@Article|:

\begin{bibexample}[label=Lefebvre1977]{{@}Article\{Lefebvre1977,…\}}
@Article{Lefebvre1977,
  author       = {Lefebvre, Henri},
  title        = {Die Produktion des städtischen Raums},
  journaltitle = {ARCH+},
  volume       = {34},
  pages        = {52--57},
  year         = {1977},
  translator   = {Franz Hiss and Hans-Ulrich Wegener},
  origlanguage = {french},
  number       = {9},
  origtitle    = {Introduction à l'espace urbain},
}
\end{bibexample}

Once again the bibliography entry alters:

\begin{bibbox}{Lefebvre1977}\footnotesize
\parbox[t]{2cm}{Lefebvre 1977} \parbox[t]{9cm}{H. Lefebvre, 
Die Produktion des stätischen Raums, \emph{Introduction à l’espace urbain}, 
{\color{red} trans. from French by F. Hiss -- H.-U. Wegener}, ARCH+ 34/9, 1977, 52–57}
\end{bibbox}

\subsubsection{inreferences}\label{inreferences}
\DescribeMacro{inreferences}  
There is the possibility to cite inreferences in the footnote as a full citations.
It is only required that the bibliography-entry is an |@Inreference|  (cf. \cref{inreference}).

Another example makes it clear: 
\begin{bibexample}[label=Nieddu1995]{{@}Inreference\{Nieddu1995,…\}}
@Inreference{Nieddu1995,
  author    = {Nieddu, Giuseppe},
  title     = {Dei Consentes},
  booktitle = LTUR-short,
  pages     = {9\psq},
  year      = {1995},
  volume    = {2},
}
\end{bibexample}

>>>>

% \draftfigure --%
%            modifying drafted figures
% Copyright (c) 2017 Lukas C. Bossert
%  
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either version 1.3
% of this license or (at your option) any later version.
% The latest version of this license is in
%   http://www.latex-project.org/lppl.txt
% and version 1.3 or later is part of all distributions of LaTeX
% version 2005/12/01 or later.
% !TEX program = lualatex
\documentclass[a4paper,
12pt,
english
]{ltxdoc}

\input{draftfigure-preamble.tex}
\newcommand\df{draftfigure\xspace}
\newcommand\dfstring{|draftfigure|\xspace}
\setkeys{Gin}{width=.3\linewidth}

\begin{document}
\title{\texttt{\df} -- \\ modifying drafted figures\footnote{%
For further information about the code visit \href{https://github.com/LukasCBossert/draftfigure}{https://github.com/LukasCBossert/draftfigure}: 
Comments and criticisms are welcome.}}
\author{Lukas C. Bossert\\{\small \href{mailto:lukas@digitales-altertum.de}{lukas@digitales-altertum.de}}}
\date{Version: \dfdate{} (\dfversion)} 
\maketitle

\begin{abstract}
\noindent This package allows you to customize the outcome of drafted figures.
\end{abstract}

%\begin{multicols}{1}
\footnotesize\parskip=0mm \tableofcontents
%\end{multicols}

\section{Installation}
\dfstring is part of the distributions MiK\TeX \footnote{Website: \url{http://www.miktex.org}.} 
and \TeX Live\footnote{Website: \url{http://www.tug.org/texlive}.}~-- thus, you
can easily install it using the respective package manager. 
If you would like to
install \dfstring manually, do the following:
Download the folder \dfstring with all relevant files from the CTAN-server\footnote{\url{https://www.ctan.org/pkg/\df}} and copy the content of the |zip|-file to the \texttt{\$LOCALTEXMF} directory of
 your system.\footnote{If you don't know what that is, have a look at
\url{http://www.tex.ac.uk/cgi-bin/texfaq2html?label=tds} or 
\url{http://mirror.ctan.org/tds/tds.html}.} 
Refresh your filename database.\footnote{ 
Here is some additional information from the UK \TeX\ FAQ:
\begin{itemize}[nosep,after=\vspace{-\baselineskip} ]
  \item \href{%
    http://www.tex.ac.uk/cgi-bin/texfaq2html?label=install-where}{%
    Where to install packages}
  \item \href{%
    http://www.tex.ac.uk/cgi-bin/texfaq2html?label=inst-wlcf}{%
    Installing files \enquote{where \LaTeX /TeX\ can find them}}
  \item \href{%
    http://www.tex.ac.uk/cgi-bin/texfaq2html?label=privinst}{%
    \enquote{Private} installations of files}
\end{itemize}
}
%%introduction from biblatex-dw copied and applied. might to be rewritten.

\clearpage
\section{Status Quo}

Usually you see all of your images in your PDF:
\begin{examplebox}
\begin{figure}[H]
  \centering
  \includegraphics{example-image-a}
  \caption{A}
  \includegraphics{example-image-b}
  \caption{B}
  \includegraphics{example-image-c}
  \caption{C}
\end{figure}
\end{examplebox}
Sometimes you do not need to see the images or want to omit them due to faster compiling or you do not have the right to publish them.

You can \enquote{switch off} the images by using the option |draft| either with 
|\documentclass[draft]|\marg{class} 
%\cs{documentclass}\oarg{draft}\marg{clss} 
or with 
|\usepackage[draft]{graphicx}|.
%\cs{usepackage}\oarg{draft}\marg{graphicx}

If you do not like the outcome with the filename and its path written with |\ttfamily| then use \dfstring.
\clearpage

\section{Usage}
 \DescribeMacro{draftfigure}  The name of the package is  \dfstring which has to be activated in the preamble.

\begin{code}
\usepackage[%
  *@\meta{further options}@*
  ]{draftfigure}
\end{code}
Without any further  Now you will now get white boxes instead of the images.
\begin{examplebox}
\begin{figure}[H]\setkeys{Gin}{draft=true}
  \centering
  \includegraphics{example-image-a}
  \caption{A}
  \includegraphics{example-image-b}
  \caption{B}
  \includegraphics{example-image-c}
  \caption{C}
\end{figure}
\end{examplebox}
\clearpage

\section{Options}

\subsection{Preamble}
\subsubsection{style}
\subsubsection{size}
\subsubsection{position}
\subsubsection{allfiguresdraft}
\subsubsection{content}
\subsubsection{filename}
\subsubsection{noframe}

\subsection{Individually possible}

You can also set |draft| to individual images.
\begin{codeexample}
\begin{figure}[H]
  \centering
  \includegraphics[draft]{example-image-a}
  \caption{A}
  \includegraphics{example-image-b}
  \caption{B}
  \includegraphics[draft]{example-image-c}
  \caption{C}
\end{figure}
\end{codeexample}

\subsubsection{style}
\subsubsection{size}
\subsubsection{position}
\subsubsection{content}
\subsubsection{filename}
\clearpage

\section{Things to work on}

- noframe for individual image\\
- combine different styles: sc and sf etc.\\
- color frame\\
- image instead of text in background\\

\end{document}
